Characterization and Photometric Performance of the Hyper Suprime-Cam Software Pipeline.

### 2017-04-30 draft/ms_v5.tex
Draft for Table2
Draft for Table3
Draft for Table4

%% ------------------------------------------------------------------------------------ %%
% Packages
\usepackage{url}
\usepackage{natbib}
\usepackage{latexsym}
\usepackage{morefloats}
\usepackage{xspace}
\usepackage[usenames, dvipsnames]{xcolor}

@@

\newcommand{\plus}{\raisebox{.4\height}{\scalebox{.6}{+}}}
\newcommand{\minus}{\raisebox{.4\height}{\scalebox{.8}{-}}}

@@

%% ------------------------------------------------------------------------------------ %%
% Table 1 : Magnitudes for PSF
\begin{table*}
    \begin{center}
    %% -------------------------------------------------------------------------------- %%
    \begin{tabular}{| c | c | c | ccccccc |}
    \hline
    Filter &   Seeing    &  Statistics & \multicolumn{7}{|c|}{Input Magnitudes (mag)} \\
    \cline{4-10}
           & FWHM ($$\asec) &             & 19.0 & 20.0 & 21.0 & 22.0 & 23.0 & 24.0 & 25.0 \\
    \hline
    $g$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        \cline{3-10}
        & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
    \hline
    $r$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        \cline{3-10}
        & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\    
    \hline
    $i$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        \cline{3-10}
        & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\    
    \hline
    $z$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        \cline{3-10}
        & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\    
    \hline
    $y$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        \cline{3-10}
        & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\    
    \hline  
    \end{tabular}
    %% -------------------------------------------------------------------------------- %%
    \end{center}
    \caption{
        \todo{Placeholder}
        Summary of the precisions and accuracies of \forced{} PSF magnitudes in all 
        five bands and in both \texttt{goodSeeing} and \texttt{badSeeing} \tracts{}.  
    }
        \label{tab:psfmag}
\end{table*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%
% Table 2 : PSF Color
\begin{table*}
    \begin{center}
    %% -------------------------------------------------------------------------------- %%
    \begin{tabular}{| c | c | c | ccccccc |}
    \hline
    Filter &   Seeing       &  Statistics & \multicolumn{4}{|c|}{Input $i$ band Magnitudes (mag)} \\
    \cline{4-10}
           & FWHM ($$\asec) &             & 19.0 & 20.0 & 21.0 & 22.0 & 23.0 & 24.0 & 25.0 \\
    \hline
    $(g-i)$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
            &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
            \cline{3-10}
            & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
            &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
    \hline
    $(i-y)$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
            &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
            \cline{3-10}
            & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
            &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\    
    \hline  
    \end{tabular}
    %% -------------------------------------------------------------------------------- %%
    \end{center}
    \caption{
        \todo{Placeholder}
        Summary of the precisions and accuracies of \forced{} PSF colors in both 
        \texttt{goodSeeing} and \texttt{badSeeing} \tracts{}.  
        We show results for both $(g-i)$ and $(i-y)$ PSF colors.
    }
        \label{tab:psfcolor}
\end{table*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%
% Table 3 : Magnitudes for cModel
\begin{table*}
    \begin{center}
    %% -------------------------------------------------------------------------------- %%
    \begin{tabular}{| c | c | c | ccccccc |}
    \hline
    Filter &   Seeing    &  Statistics & \multicolumn{7}{|c|}{Input Magnitudes (mag)} \\
    \cline{4-10}
           & FWHM ($$\asec) &             & 19.0 & 20.0 & 21.0 & 22.0 & 23.0 & 24.0 & 25.0 \\
    \hline
    $g$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        \cline{3-10}
        & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
    \hline
    $r$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        \cline{3-10}
        & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\    
    \hline
    $i$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        \cline{3-10}
        & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\    
    \hline
    $z$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        \cline{3-10}
        & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\    
    \hline
    $y$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        \cline{3-10}
        & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\    
    \hline  
    \end{tabular}
    %% -------------------------------------------------------------------------------- %%
    \end{center}
    \caption{
        \todo{Placeholder}
        Summary of the precisions and accuracies of \forced{} \cmodel{} magnitudes in 
        all five bands and in both \texttt{goodSeeing} and \texttt{badSeeing} \tracts{}.  
    }
        \label{tab:psfmag}
\end{table*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%
% Table 4 : CModel Color
\begin{table*}
    \begin{center}
    %% -------------------------------------------------------------------------------- %%
    \begin{tabular}{| c | c | c | ccccccc |}
    \hline
    Filter &   Seeing       &  Statistics & \multicolumn{4}{|c|}{Input $i$ band Magnitudes (mag)} \\
    \cline{4-10}
           & FWHM ($$\asec) &             & 19.0 & 20.0 & 21.0 & 22.0 & 23.0 & 24.0 & 25.0 \\
    \hline
    $(g-i)$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
            &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
            \cline{3-10}
            & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
            &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
    \hline
    $(i-y)$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
            &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
            \cline{3-10}
            & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
            &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\    
    \hline  
    \end{tabular}
    %% -------------------------------------------------------------------------------- %%
    \end{center}
    \caption{
        \todo{Placeholder}
        Summary of the precisions and accuracies of \forced{} \cmodel{} colors in both 
        \texttt{goodSeeing} and \texttt{badSeeing} \tracts{}.  
        We show results for both $(g-i)$ and $(i-y)$ PSF colors.
    }
        \label{tab:cmodelcolor}
\end{table*}
%% ------------------------------------------------------------------------------------ %%

>>>>

%% ------------------------------------------------------------------------------------ %%
% Packages
\usepackage{url}
\usepackage{natbib}
\usepackage{latexsym}
\usepackage{morefloats}
\usepackage{xspace}
\usepackage[usenames, dvipsnames]{xcolor}
\usepackage{colortbl}
\usepackage{multirow}

@@

\newcommand{\plus}{\raisebox{.4\height}{\scalebox{.6}{+}}}
\newcommand{\minus}{\raisebox{.4\height}{\scalebox{.8}{-}}}
\newcommand{\smag}{$\sigma_{\Delta\mathrm{mag}}$}
\newcommand{\mmag}{$\left<{\Delta\mathrm{mag}}\right>$}
\newcommand{\n}{$\minus$}

@@

%% ------------------------------------------------------------------------------------ %%
% Table 1 : Magnitudes for PSF
\begin{table*}
    \begin{center}
    %% -------------------------------------------------------------------------------- %%
    \begin{tabular}{| c | c | c | ccccccc |}
    \hline
    Filter &   Seeing    &  Statistics & \multicolumn{7}{|c|}{Input Magnitudes (mag)} \\
    \cline{4-10}
           & FWHM ($$\asec) &             & 19.0 & 20.0 & 21.0 & 22.0 & 23.0 & 24.0 & 25.0 \\
    \hline
    $g$ & 0.45 & \smag{} & 0.016 & 0.017 & 0.019 & 0.023 & 0.029 & 0.043 & 0.078 \\
        &      & \mmag{}  & 0.008 & 0.009 & 0.009 & 0.009 & 0.008 & 0.007 & $\minus 0.003$ \\
        \cline{3-10}
        & 0.70 & \smag{} & 0.016 & 0.018 & 0.019 & 0.021 & 0.026 & 0.039 & 0.091 \\
        &      & \mmag{}  & 0.007 & 0.006 & 0.006 & 0.005 & 0.004 & 0.003 & $\minus 0.002$ \\
    \hline
    $r$ & 0.45 & \smag{} & 0.021 & 0.023 & 0.024 & 0.025 & 0.027 & 0.035 & 0.064 \\
        &      & \mmag{}  & 0.011 & 0.011 & 0.012 & 0.011 & 0.012 & 0.011 & 0.011 \\
        \cline{3-10}
        & 0.70 & \smag{} & 0.026 & 0.029 & 0.031 & 0.034 & 0.041 & 0.054 & 0.090 \\
        &      & \mmag{}  & 0.009 & 0.009 & 0.009 & 0.009 & 0.009 & 0.006 & 0.001 \\    
    \hline
    $i$ & 0.45 & \smag{} & 0.015 & 0.015 & 0.017 & 0.018 & 0.020 & 0.030 & 0.047 \\
        &      & \mmag{}  & 0.002 & 0.002 & 0.002 & 0.002 & 0.002 & 0.002 & 0.003 \\
        \cline{3-10}
        & 0.70 & \smag{} & 0.012 & 0.013 & 0.014 & 0.016 & 0.022 & 0.043 & 0.050 \\
        &      & \mmag{}  & 0.001 & 0.002 & 0.002 & 0.002 & 0.002 & 0.001 & $\minus 0.012$ \\    
    \hline
    $z$ & 0.45 & \smag{} & 0.011 & 0.013 & 0.014 & 0.016 & 0.025 & 0.053 & 0.094 \\
        &      & \mmag{}  & 0.002 & 0.002 & 0.002 & 0.003 & 0.003 & 0.005 & $\minus 0.001$ \\
        \cline{3-10}
        & 0.70 & \smag{} & 0.019 & 0.020 & 0.021 & 0.024 & 0.038 & 0.071 & 0.104 \\
        &      & \mmag{}  & 0.003 & 0.003 & 0.003 & 0.004 & 0.005 & 0.003 & $\minus 0.010$ \\    
    \hline
    $y$ & 0.45 & \smag{} & 0.017 & 0.017 & 0.021 & 0.033 & 0.074 & 0.138 & -- \\
        &      & \mmag{}  & 0.006 & 0.006 & 0.006 & 0.006 & 0.000 & $\minus 0.001$ & -- \\
        \cline{3-10}
        & 0.70 & \smag{} & 0.019 & 0.019 & 0.023 & 0.037 & 0.077 & 0.153 & -- \\
        &      & \mmag{}  & 0.007 & 0.008 & 0.008 & 0.006 & 0.003 & $\minus 0.034$ & -- \\    
    \hline  
    \end{tabular}
    %% -------------------------------------------------------------------------------- %%
    \end{center}
    \caption{
        \todo{Placeholder}
        Summary of the \smag{}s and accuracies of \forced{} PSF magnitudes in all 
        five bands and in both \texttt{goodSeeing} and \texttt{badSeeing} \tracts{}.  
    }
        \label{tab:psfmag}
\end{table*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%
% Table 2 : PSF Color
\begin{table*}
    \begin{center}
    %% -------------------------------------------------------------------------------- %%
    \begin{tabular}{| c | c | c | ccccccc |}
    \hline
    Filter &   Seeing       &  Statistics & \multicolumn{4}{|c|}{Input $i$ band Magnitudes (mag)} \\
    \cline{4-10}
           & FWHM ($$\asec) &             & 19.0 & 20.0 & 21.0 & 22.0 & 23.0 & 24.0 & 25.0 \\
    \hline
    $(g-i)$ & 0.45 & \smag{} & 0.023 & 0.026 & 0.037 & 0.054 & 0.077 & 0.105 & 0.117 \\
            &      & \mmag{}  & 0.008 & 0.007 & 0.005 & 0.003 & $\minus 0.002$ & $\minus 0.009$ & $\minus 0.035$ \\
            \cline{3-10}
            & 0.70 & \smag{} & 0.021 & 0.025 & 0.033 & 0.051 & 0.075 & 0.105 & 0.137 \\
            &      & \mmag{}  & 0.004 & 0.003 & 0.002 & 0.001 & $\minus 0.001$ & $\minus 0.002$ & 0.007 \\
    \hline
    $(i-y)$ & 0.45 & \smag{} & 0.019 & 0.020 & 0.022 & 0.031 & 0.058 & 0.109 & 0.189 \\
            &      & \mmag{}  & $\minus 0.004$ & $\minus 0.004$ & $\minus 0.004$ & $\minus 0.004$ & $\minus 0.002$ & 0.011 & 0.064 \\
            \cline{3-10}
            & 0.70 & \smag{} & 0.019 & 0.020 & 0.021 & 0.031 & 0.057 & 0.123 & 0.221 \\
            &      & \mmag{}  & $\minus 0.006$ & $\minus 0.006$ & $\minus 0.006$ & $\minus 0.005$ & $\minus 0.005$ & $\minus 0.002$ & $\minus 0.064$ \\    
    \hline  
    \end{tabular}
    %% -------------------------------------------------------------------------------- %%
    \end{center}
    \caption{
        \todo{Placeholder}
        Summary of the \smag{}s and accuracies of \forced{} PSF colors in both 
        \texttt{goodSeeing} and \texttt{badSeeing} \tracts{}.  
        We show results for both $(g-i)$ and $(i-y)$ PSF colors.
    }
        \label{tab:psfcolor}
\end{table*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%
% Table 3 : Magnitudes for cModel
\begin{table*}
    \begin{center}
    %% -------------------------------------------------------------------------------- %%
    \begin{tabular}{| c | c | c | cccccc |}
    \hline
    Filter & Seeing & Statistics & \multicolumn{6}{|c|}{Input Magnitudes (mag)} \\
    \cline{4-9}
           & FWHM ($$\asec) &             & 20.0 & 21.0 & 22.0 & 23.0 & 24.0 & 25.0 \\
    \hline
    $g$ & 0.45 & \smag{} & 0.111 & 0.156 & 0.161 & 0.152 & 0.176 & 0.196 \\
        &      & \mmag{}  & $\minus 0.060$ & $\minus 0.036$ & $\minus 0.004$ & 0.021 & 0.009 & $\minus 0.005$ \\
        \cline{3-9}
        & 0.70 & \smag{} & 0.137 & 0.161 & 0.138 & 0.147 & 0.181 & 0.202 \\
        &      & \mmag{}  & 0.018 & $\minus 0.008$ & 0.029 & 0.040 & 0.028 & 0.012 \\
    \hline
    $r$ & 0.45 & \smag{} & 0.197 & 0.151 & 0.147 & 0.167 & 0.179 & 0.211  \\
        &      & \mmag{}  & $\minus0.036$ & $\minus 0.015$ & 0.033 & 0.033 & 0.017 & 0.012  \\
        \cline{3-9}
        & 0.70 & \smag{} & 0.167 & 0.119 & 0.142 & 0.168 & 0.189 & 0.232 \\
        &      & \mmag{}  & $\minus 0.024$ & 0.023 & 0.050 & 0.036 & 0.025 & 0.022 \\    
    \hline
    $i$ & 0.45 & \smag{} & 0.173 & 0.157 & 0.154 & 0.168 & 0.183 & 0.218 \\
        &      & \mmag{}  & $\minus 0.023$ & 0.008 & 0.004 & 0.017 & $\minus 0.001$ & $\minus 0.006$ \\
        \cline{3-9}
        & 0.70 & \smag{} & 0.154 & 0.157 & 0.153 & 0.174 & 0.193 & 0.246 \\
        &      & \mmag{}  & 0.017 & 0.043 & 0.040 & 0.021 & 0.003 & $\minus 0.013$ \\
    \hline
    $z$ & 0.45 & \smag{} & 0.171 & 0.176 & 0.165 & 0.182 & 0.201 & 0.241 \\
        &      & \mmag{}  & $\minus0.006$ & 0.042 & 0.038 & 0.018 & $\minus 0.002$ & $\minus 0.012$ \\
        \cline{3-9}
        & 0.70 & \smag{} & 0.168 & 0.155 & 0.167 & 0.185 & 0.222 & 0.278 \\
        &      & \mmag{}  & 0.027 & 0.046 & 0.045 & 0.028 & 0.009 & $\minus 0.034$ \\    
    \hline
    $y$ & 0.45 & \smag{} & 0.179 & 0.169 & 0.178 & 0.197 & 0.241 & 0.308 \\
        &      & \mmag{}  & 0.011 & 0.056 & 0.044 & 0.014 & $\minus 0.067$ & $\minus 0.244$ \\
        \cline{3-9}
        & 0.70 & \smag{} & 0.169 & 0.164 & 0.169 & 0.194 & 0.253 & 0.315 \\
        &      & \mmag{}  & 0.041 & 0.052 & 0.048 & 0.020 & $\minus 0.057$ & $\minus 0.299$ \\    
    \hline  
    \end{tabular}
    %% -------------------------------------------------------------------------------- %%
    \end{center}
    \caption{
        \todo{Placeholder}
        Summary of the \smag{}s and accuracies of \forced{} \cmodel{} magnitudes in 
        all five bands and in both \texttt{goodSeeing} and \texttt{badSeeing} \tracts{}.  
    }
        \label{tab:psfmag}
\end{table*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%
% Table 4 : CModel Color
\begin{table}
    \begin{center}
    %% -------------------------------------------------------------------------------- %%
    %\begin{tabular}{| c | c | c | cccccc |}
    \begin{tabular}{| c | c | c | c | c | c | }
    \hline
    \multirow{2}{*}{$i_{\mathrm{Input}}$} & Color & \multicolumn{2}{|c|}{$(g-i)$} & \multicolumn{2}{|c|}{$(i-y)$} \\
    \cline{2-6}
      & FWHM & $0.45$\asec{} & $0.70$\asec{} & $0.45$\asec{} & $0.70$\asec{} \\
    \hline
    (mag) & & (mag) & (mag) & (mag) & (mag) \\
    \hline \hline
    \rowcolor[gray]{.85} 20.0 & \smag{} &   0.068 & 0.051 &   0.072 &   0.046 \\
    \rowcolor[gray]{.85}      & \mmag{} &   0.013 & 0.002 & \n0.006 & \n0.001 \\
    \hline 
    \rowcolor[gray]{1.0} 21.0 & \smag{} &   0.080 & 0.059 &   0.062 &   0.040 \\
    \rowcolor[gray]{1.0}      & \mmag{} &   0.010 & 0.003 & \n0.003 & \n0.004 \\
    \hline
    \rowcolor[gray]{.85} 22.0 & \smag{} &   0.089 & 0.072 &   0.071 &   0.059 \\
    \rowcolor[gray]{.85}      & \mmag{} &   0.002 & 0.002 & \n0.005 & \n0.007 \\
    \hline
    \rowcolor[gray]{1.0} 23.0 & \smag{} &   0.105 & 0.090 &   0.109 &   0.103 \\
    \rowcolor[gray]{1.0}      & \mmag{} & \n0.018 & 0.001 & \n0.002 & \n0.005 \\
    \hline
    \rowcolor[gray]{.85} 24.0 & \smag{} &   0.136 & 0.127 &   0.175 &   0.170 \\
    \rowcolor[gray]{.85}      & \mmag{} & \n0.008 & 0.006 &   0.012 & \n0.007 \\
    \hline
    \rowcolor[gray]{1.0} 25.0 & \smag{} &   0.179 & 0.185 &   0.227 &   0.241 \\
    \rowcolor[gray]{1.0}      & \mmag{} & \n0.003 & 0.019 &   0.053 &   0.006 \\
    \hline
    \end{tabular}
    %% -------------------------------------------------------------------------------- %%
    \end{center}
    \caption{
        \todo{Placeholder}
        Summary of the precisions and accuracies of \forced{} \cmodel{} colors in both 
        \texttt{goodSeeing} and \texttt{badSeeing} \tracts{}.  
        We show results for both $(g-i)$ and $(i-y)$ PSF colors.
    }
        \label{tab:cmodelcolor}
\end{table}
%% ------------------------------------------------------------------------------------ %%
